Catchability_ecov_sims

### 2022-12-16 Ecov_study/catchability/Catchability_ecov_sims.Rmd
Update results overview figure, add code to postprocess multiple simulation results files.

        for(isim in 1:nsim){ # Loop over simulations
                for(iEM in 1:length(inputEMlist)){ # Loop over estimation models
                        # Pull EM initial input from list
                        inputEM <- inputEMlist[[iEM]]

@@

                        # Store model-specific results for given isim here (append EM results to storage list for that EM)
                        storeEM[which(namesEM == namesEM[iEM])][[1]] <- append(storeEM[which(namesEM == namesEM[iEM])], list(resultEM))

@@

digraph boxes_and_circles{
## Add node statements
# Define shape
node[shape = box]
OM[label = 'OM \n results$OM']
sim1[label = 'Simulation 1 results \n results$OM[[1]]']
sim2[label = 'Simulation 1 results \n results$OM[[2]]']
sim3[label = 'Simulation 1 results \n results$OM[[3]]']

EM1[label = 'EM1 \n results$EM1']
sim1_1[label = 'Simulation 1 results \n results$EM1[[1]]']
sim1_2[label = 'Simulation 1 results \n results$EM1[[1]]']
sim1_3[label = 'Simulation 1 results \n results$EM1[[1]]']
EM2[label = 'EM2 \n results$EM2']
sim2_1[label = 'Simulation 1 results \n results$EM2[[1]]']
sim2_2[label = 'Simulation 1 results \n results$EM2[[1]]']
sim2_3[label = 'Simulation 1 results \n results$EM2[[1]]']
ageslab[label = 'ages.lab']

@@

## Post-process results
```{r}
#' @param filenames A vector of strings (including .Rda extensions) indicating what Rdata results files to read in and post process
#' 
#' @return

postprocess_simTestWHAM <- function(filenames = NULL){
        # Set up storage for processed results

        # Loop over files
        for(ifile in 1:length(filenames)){
                # Read in Rdata object
                fileDat <- readRDS(filenames[ifile])

                nsim <- # Based on length of results in given filename

                # Loop over simulations in each file
                for(isim in 1:nsim){
                        # Calculate performance metrics here & add to storage
                }

        } # End loop over filenames
}
```

>>>>

        for(isim in 1:nsim){ # Loop over simulations
          print(paste0("Simulation_", isim))
                for(iEM in 1:length(inputEMlist)){ # Loop over estimation models
                        # Pull EM initial input from list
                        inputEM <- inputEMlist[[iEM]]

@@

                        # Store model-specific results for given isim here (append EM results to storage list for that EM)
                        storeEM[which(namesEM == namesEM[iEM])][[1]] <- append(storeEM[which(namesEM == namesEM[iEM])][[1]], list(resultEM))

@@

digraph boxes_and_circles{
## Add node statements
# Define shape
node[shape = box]
OM[label = 'OM \n results$OM']
sim1[label = 'Simulation 1 results \n results$OM[1][[1]]']
sim2[label = 'Simulation 2 results \n results$OM[2][[1]]']
sim3[label = 'Simulation 3 results \n results$OM[3][[1]]']

EM1[label = 'EM1 \n results$EM1']
sim1_1[label = 'Simulation 1 results \n results[EMs[1]][[1]][1][[1]]']
sim1_2[label = 'Simulation 2 results \n results[EMs[1]][[1]][2][[1]]']
sim1_3[label = 'Simulation 3 results \n results[EMs[1]][[1]][2][[1]]']
EM2[label = 'EM2 \n results$EM2']
sim2_1[label = 'Simulation 1 results \n results[EMs[2]][[1]][1][[1]]']
sim2_2[label = 'Simulation 2 results \n results[EMs[2]][[1]][2][[1]]']
sim2_3[label = 'Simulation 3 results \n results[EMs[2]][[1]][3][[1]]']
ageslab[label = 'ages.lab']

@@

## Post-process results
```{r}
#' @param filenames A vector of strings (including .RData extensions) indicating what results files to read in and post process
#' 
#' @return A dataframe containing the following columns describing model performance
#' \itemize{
#'   \item{Year - Year associated with performance metric}
#'   \item{sim - Simulation number (based on total number of simulations in all files processed)}
#'   \item{EM - Name of estimation model used to calculate performance metric}
#'   \item{converged - Boolean indicating whether model converged with invertible hessian ("Yes") or not ("No")}
#'   \item{relSSB - Ratio of SSB from EM:OM}
#'   \item{relF - Ratio of F from EM:OM}
#'   \item{relR - Ratio of R from EM:OM}
#'   \item{relEcov_x - Ratio of Ecov_x from EM:OM}
#' }

postprocess_simTestWHAM <- function(filenames = NULL){
  # Set up storage for processed results
  perfMet <- NULL

  # Establish total number of simulations across all files (based on nsim in filename)
  nsim <- rep(NA, length(filenames))
  for(ifile in 1:length(filenames)){
    fileSpecs <- strsplit(filenames[ifile], "_")
    nsim[ifile] <- fileSpecs[[1]][which(grepl("simWHAM", fileSpecs[[1]]))+1] %>% as.numeric()
  }

  nsim <- c(0, nsim) # Add 0 so isim indexing in file processed output goes from 1:total nsim

  # Loop over files to calculate performance metrics
  for(ifile in 1:length(filenames)){
    # Read in RData object
    load(file=filenames[ifile]) # loads object named "results"

    # Loop over simulations in each file
    for(isim in 1:nsim[ifile+1]){ # start at ifile+1 since nsim[ifile] = 0 for sim numbering reasons

      # Pull out EM names 
      EMs <- names(results)[2:length(names(results))]

      # Loop over EM in each ifile
      for(iEM in 1:length(EMs)){

        # Store Years, isim, iEM, convergence (mod$opt$convergence == 0 and hessian invertible $na_sdrep == FALSE)
        Year <- results[EMs[iEM]][[1]][isim][[1]]$years
        sim <- rep((isim+nsim[ifile]), length(Year)) # + 0 for first file, starts sim numbering at nsim[ifile=1]+1 for second file
        EM <- rep(EMs[iEM], length(Year))
        if(check_convergence(results[EMs[iEM]][[1]][isim][[1]], ret=TRUE)$na_sdrep == TRUE){
          converged <- rep("No", length(Year))
        } else{
          converged <- rep("Yes", length(Year))
        }

        # Proportion of EM:OM SSB
          # EM SSB calculated based on plotting script https://github.com/timjmiller/wham/blob/6c30301d5b68c2bb0c0330cc4f112432c7950dfd/R/wham_plots_tables.R#L725-L738
        tempSSB_EM <- results[EMs[iEM]][[1]][isim][[1]]$sdrep %>% summary() #EM SSB must be calculated, this line triggers an NaNs produced warning for EMs that didn't converge with invertible hessians
        tempSSB_EM <- tempSSB_EM[rownames(tempSSB_EM) == "log_SSB",]
        tempSSB_EM <- exp(cbind(tempSSB_EM, tempSSB_EM[,1]+qnorm(0.975)*cbind(-tempSSB_EM[,2], tempSSB_EM[,2])))#/1000 Don't divide by 1000 so units in mt rather than kmt
        tempSSB_EM <- tempSSB_EM[,1] 
          # OM SSB
        tempSSB_OM <- results$OM[isim][[1]]$SSB # Pull SSB directly from simulated data
          # relative SSB
        relSSB <- tempSSB_EM/tempSSB_OM

        # Proportion of EM:OM F
          # EM calculated F based on plotting scripts
        mod <- results[EMs[iEM]][[1]][isim][[1]]
        std = results[EMs[iEM]][[1]][isim][[1]]$sdrep %>% summary()
        years_full <- mod$years_full
        n_ages = mod$env$data$n_ages
        faa.ind <- which(rownames(std) == "log_FAA_tot")
        log.faa <- matrix(std[faa.ind,1], length(years_full), n_ages)
        faa.cv <- matrix(std[faa.ind,2], length(years_full), n_ages)
        age.full.f <- apply(log.faa,1, function(x) max(which(x == max(x))))
        full.f.ind = cbind(1:length(years_full), age.full.f)
        log.full.f <- log.faa[full.f.ind]
        full.f.cv <- faa.cv[full.f.ind]
        full.f <- exp(log.full.f)
          # OM F
        tempF_OM <- c(results$OM[isim][[1]]$F)
          # relative F
        relF <- full.f/tempF_OM

        # Proportion of EM:OM Recruitment 
          # EM R calculated based on plotting script: https://github.com/timjmiller/wham/blob/6c30301d5b68c2bb0c0330cc4f112432c7950dfd/R/wham_plots_tables.R#L765-L780
        tempR_EM <-  results[EMs[iEM]][[1]][isim][[1]]$sdrep %>% summary()
        ind <- rownames(tempR_EM) == "log_NAA_rep"
        tempR_EM <-  exp(array(tempR_EM[ind,1], dim = c(length(results[EMs[iEM]][[1]][isim][[1]]$years), 8)))
        tempR_EM <- tempR_EM[,1]
          # OM recruitment
        tempR_OM <- results$OM[isim][[1]]$NAA[,1] 
          # relative R
        relR <- tempR_EM/tempR_OM

        # Relative Ecov_x values (EM:OM ratio)
        if("TRUE" %in% (results[EMs[iEM]][[1]][isim][[1]]$input$data$Ecov_where > 0)){ # If link to ecov specified in EM calculate EM:OM ratio for Ecov_x values
            # EM
        tempEcovx_EM <- results[EMs[iEM]][[1]][isim][[1]]$sdrep %>% summary() 
        tempEcovx_EM <- tempEcovx_EM[rownames(tempEcovx_EM)=="Ecov_x",]
          # OM
        tempEcovx_OM <- results$OM[isim][[1]]$Ecov_x
          # Relative Ecov_x
        relEcov_x <- tempEcovx_EM[,"Estimate"]/tempEcovx_OM
        } else{ # If no ecov link specified then save an NA for that model in all years 
          relEcov_x <- rep(NA, length(Year))
        }

        # # Relative Ecov_beta (EM:OM ratio) for all four indices
        #   # EM
        # tempEcovbeta_EM <- results[EMs[iEM]][[1]][isim][[1]]$sdrep %>% summary()
        # tempEcovbeta_EM <- tempEcovbeta_EM[rownames(tempEcovbeta_EM)=="Ecov_beta"]
        #   # OM
        # tempEcovbeta_OM <- results$OM[isim][[1]]$Ecov_beta # by age rather than by index?
        #

        # Store results
          # EM perfMets
          EMperfMets <- cbind(Year, sim, EM, converged, relSSB, relF, relR, relEcov_x)

          # Append perfMets to storage
          perfMet <- rbind(perfMet, EMperfMets)

      } # End loop over EM

    } # End loop over simulations in ifile

  } # End loop over filenames

  # Clean table rownames and ensure that numeric results are not treated as strings
  rownames(perfMet) <- NULL
  colnames(perfMet) <- c("Year", "sim", "EM", "converged", "relSSB", "relF", "relR", "relEcov_x")
  perfMet <- perfMet %>% as.data.frame() %>% 
    dplyr::summarise(Year = as.numeric(Year),
                     sim = as.numeric(sim),
                     EM = EM,
                     converged = converged,
                     relSSB = as.numeric(relSSB),
                     relF = as.numeric(relF),
                     relR = as.numeric(relR),
                     relEcov_x = as.numeric(relEcov_x))

  return(perfMet)
}
```
